Improved Bounds for Online Balanced Repartitioning

### 2020-04-22 paper/disc20clustering.tex
Migration graph characterization

\subsection{Characterization of the reconfiguration graph}

\maciek{I'll write it some day. Maciek.}

Describe the graph. Edges and labels.

\subsection{Costly reconfiguration example}

@@

\subsection{Cascade bounds and an improved algorithm for general k, l}

@@

\begin{proof}

>>>>

\subsection{Characterization of the migration graph}

Consider a component merge action performed by \TAlg that triggers a reconfiguration from a configuration $C_I$ to a configuration $C_F$.
To execute the reconfiguration, the nodes of two non-collocated components migrate to a common cluster.
Each cluster contains exactly $k$ nodes, thus other nodes migrate to take the place of nodes of merged components.
Their place must be occupied, too, and this way a single merge action may trigger migrations in clusters not directly involved in a merge action (for an example, see Section~\ref{ssec:example}). 
Recall that both $C_I$ and $C_F$ are component-respecting configurations, hence a migration of a single node entails migrations of all nodes of its cluster.

In Section~\ref{ssec:cascade}, we upper bound the cost incurred by a reconfiguration that follows a single component merge.
To this end, we introduce a \emph{migration graph} that models the reconfiguration.
In the following, we characterize the structure of the migration graph.

\noindent
\textbf{Vertices.}
The vertices of the migration graph are all $\ell$ clusters of the instance.
We distinguish the \emph{core vertices} that correspond to clusters directly involved in the merge operation: the clusters containing the to-be-merged components in $C_I$ and the cluster containing the merged component in $C_F$.
There are at most $3$ core vertices in each migration graph (at most two components participate in the merge, and these may migrate to a third cluster).

\noindent
\textbf{Edges and their labels.}

Cost of cluster reconfiguration is the number of exchanged nodes, and from the standpoind of a migration graph, it is the sum of labels on edges of the graph.
It is bounded by $2k$ times the size of the connected component.

Core of the graph and the component merge.

Multiple migration graphs for a component merge exist, and multiple of them might have the optimal cost.
In Section \ref{ssec:cascade}, we show that among all migration graphs for given component merge, there exists an optimal graph with the bounded path length.

\subsection{Costly cluster reconfiguration example}
\label{ssec:example}

@@

\subsection{Bounds on the size of a cluster reconfiguration graph}
\label{ssec:cascade}

@@

\begin{proof}
  Assume that there exists a cluster reconfiguration
